---
title: "Exercises: 06-15-20"
author: "Shawn Santo"
date: ""
output: 
  html_document:
    css: "exercises.css"
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Packages

```{r}
library(lobstr)
library(tidyverse)
library(lubridate)
library(multidplyr)
```

# Exercise 1 {.tabset .tabset-fade .tabset-pills}

## Problem

Can you diagnose what is going on below?

```{r}
x <- 1:10
y <- x

tracemem(x)
c(obj_addr(x), obj_addr(y))

y[1] <- 3
```

## Solution

The question is, why are two copies being made? The vector `x` is of type
integer. However, when we do subassignment and change the first component of
`y` to be 3 (of type double) two copies are made. One for the modification of 
the component, the other for the atomic vector type change.

```{r}
x <- 1:10
y <- x

tracemem(x)
c(obj_addr(x), obj_addr(y))

y[1] <- 3L # type integer
```


# Exercise 2 {.tabset .tabset-fade .tabset-pills}

## Problem

Starting from 0 we can see that

```{r}
lobstr::obj_size(integer(0))
lobstr::obj_size(numeric(0))
```

are both 48 bytes. Run the code below and see if you can deduce how 
R handles these numeric data in memory?

```{r eval=FALSE}
diff(sapply(0:100, function(x) obj_size(integer(x))))
```

```{r eval=FALSE}
c(obj_size(integer(20)), obj_size(integer(22)))
```

```{r eval=FALSE}
diff(sapply(0:100, function(x) obj_size(numeric(x))))
```

```{r eval=FALSE}
c(obj_size(numeric(10)), obj_size(numeric(14)))
```

## Solution

R allocates memory to vectors in chunks. An integer vector of length one is
allocated 56 bytes, 8 more than a null integer vector. Since an integer
component only requires 4 bytes of memory, an integer vector of length two is
also only 56 bytes. R does not need any more memory. Hence, we see that
`obj_size(integer(1))` and `obj_size(integer(2))` are the same. The `diff()`
function calls give you an idea as to how memory is allocated in chunks.

# Exercise 3 {.tabset .tabset-fade .tabset-pills}

## Problem

Start with the below code to create a partitioned data frame spread across
three clusters.

```{r eval=FALSE}
clust <- new_cluster(3)

base_url <- "http://www2.stat.duke.edu/~sms185/data/bike/"
files <- c("cbs_2015.csv", "cbs_2016.csv", "cbs_2017.csv")

cluster_assign_partition(clust, file_name = str_c(base_url, files))
cluster_send(clust, cbs_data <- vroom::vroom(file_name))

cbs <- party_df(clust, "cbs_data")
```

1. Bring the three tibbles together with `collect()`.

2. Fix the names with `janitor::clean_names()`.

3. Add a variable `year`.

4. Partition the tibble onto three clusters grouped by `year`. Check you have
   `Shards: 3 [3,185,906--3,757,777 rows]`.

5. Use `lubridate::month()`, `lubridate::day()` and `lubridate::wday()`
   to parse `start_date` and `end_date`, and include the new variables in
   the tibble.
   
6. Compute the median ride duration for each year-month-wday combination; bring
   everything back together as an object named `cbs`.
   
## Solution

```{r eval=FALSE}
cbs <- cbs %>% 
  collect()

cbs <- janitor::clean_names(cbs) %>% 
  mutate(year = str_extract(start_date, pattern = "\\d{4}"))

clust <- new_cluster(3)
cbs_year <- cbs %>% 
  group_by(year) %>% 
  partition(clust)

cbs <- cbs_year %>% 
  mutate(start_month = lubridate::month(start_date),
         start_day   = lubridate::day(start_date),
         start_wday  = lubridate::wday(start_date, label = TRUE),
         end_month   = lubridate::month(end_date),
         end_day     = lubridate::day(end_date),
         end_wday    = lubridate::wday(end_date, label = TRUE)
         ) %>% 
  group_by(year, start_month, start_wday) %>% 
  summarise(med = median(duration)) %>% 
  collect()
```