---
title: "Exercises: 06-17-20"
author: "Shawn Santo"
date: ""
output: 
  html_document:
    css: "exercises.css"
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Packages

```{r}
library(bench)
library(parallel)
library(tidyverse)
```

# Exercise 1 {.tabset .tabset-fade .tabset-pills}

## Problem

Which function reads in CSV files quickest?

- `read.csv()`

- `readr::read_csv()`

- `data.table::fread()`

Test them with http://bit.ly/nz-data and the 
2013 capital bike share data available at
http://www2.stat.duke.edu/~sms185/data/bike/cbs_2013.csv.

## Solution

```{r cache=TRUE}
nz_link <- "http://bit.ly/nz-data"

bench_time({
  read.csv(nz_link)
})

bench_time({
  readr::read_csv(nz_link)
})

bench_time({
  data.table::fread(nz_link)
})

bike_link <- "http://www2.stat.duke.edu/~sms185/data/bike/cbs_2013.csv"

bench_time({
  read.csv(bike_link)
})

bench_time({
  readr::read_csv(bike_link)
})

bench_time({
  data.table::fread(bike_link)
})
```

# Exercise 2 {.tabset .tabset-fade .tabset-pills}

## Problem

Do you notice anything strange with objects `result2` and `result4`? 
What is going on?

```{r}
detectCores()

result2 <- mclapply(1:12, FUN = function(x) rnorm(1), 
                   mc.cores = 2, mc.set.seed = FALSE) %>% 
  unlist()

result2
```

```{r}
result4 <- mclapply(1:12, FUN = function(x) rnorm(1), 
                   mc.cores = 4, mc.set.seed = FALSE) %>% 
  unlist()

result4
```

## Solution

When `mc.set.seed = FALSE`, the child process has the same initial random 
number generator (RNG) state as the current R session. Hence, we see the same
numbers generated two times and four times when we use two and four cores,
respectively.

# Exercise 3 {.tabset .tabset-fade .tabset-pills}

## Problem

Parallelize the four expressions below.

```{r eval=FALSE}
{mtcars %>% 
  count(cyl)}

{mtcars %>% 
  lm(mpg ~ wt + hp + factor(cyl), data = .)}

{map_chr(mtcars, typeof)}

{mtcars %>% 
  select(mpg, disp:qsec) %>% 
  map_df(summary)} 
```

## Solution

```{r}
x <- list()

x$expr1 <- mcparallel({
  mtcars %>% 
  count(cyl)
})

x$expr2 <- mcparallel({
  mtcars %>% 
    lm(mpg ~ wt + hp + factor(cyl), data = .)
})

x$expr3 <- mcparallel({
  map_chr(mtcars, typeof)
})

x$expr4 <- mcparallel({
  mtcars %>% 
    select(mpg, disp:qsec) %>% 
    map_df(summary)
})
```

```{r}
mccollect(x)
```

