---
title: "Exercises: 05-13-20"
author: "Shawn Santo"
date: ""
output: 
  html_document:
    css: "exercises.css"
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Exercise 1 {.tabset .tabset-fade .tabset-pills}

## Problem

What does each of the following return? Run the code to check your answer.

```{r eval=FALSE}
if (1 == "1") "coercion  works" else "no coercion "

ifelse(5 > c(1, 10, 2), "hello", "olleh")
```

## Solution

```{r}
if (1 == "1") "coercion  works" else "no coercion "
ifelse(5 > c(1, 10, 2), "hello", "olleh")
```

# Exercise 2 {.tabset .tabset-fade .tabset-pills}

## Problem

Consider two vectors, `x` and `y`, each of length one. Write a set of
   conditionals that satisfy the following.
   
- If `x` is positive and `y` is negative or `y` is positive and `x` is
  negative, print "knits".
- If `x` divided by `y` is positive, print "stink".
- Stop execution if `x` or `y` are zero.
    
Test your code with various `x` and `y` values. Where did you
place the stop execution code?

## Solution

```{r}
x <- 4
y <- -10

if (x == 0 | y == 0) {
  stop("One of x or y is 0!")
} else if (x / y > 0) {
  print("stink")
} else {
  print("knits")
}
```

# Exercise 3 {.tabset .tabset-fade .tabset-pills}

## Problem

Consider the vector `x` below.

```{r eval=FALSE}
x <- c(3, 4, 12, 19, 23, 49, 100, 63, 70)
```
    
Write R code that prints the perfect squares in `x`.

## Solution

```{r}
x <- c(3, 4, 12, 19, 23, 49, 100, 63, 70)

for (i in x) {
  if (sqrt(i) %% 1) {
    next
  }
  print(i)
}
```

# Exercise 4 {.tabset .tabset-fade .tabset-pills}

## Problem

Consider `z <- c(-1, .5, 0, .5, 1)`. Write R code that prints
the smallest non-negative integer $k$ satisfying the inequality
$$\lvert cos(k) - z \rvert < 0.001$$
for each component of `z`.

## Solution

```{r}
for (z in c(-1, .5, 0, .5, 1)) {
  k <- 0
  while (abs(cos(k) - z) >= .001) {
    k <- k + 1
  }
  print(k)
}
```
